% !TEX encoding = UTF-8
% !TEX TS-program = pdflatex
% !TEX root = ../Tesi.tex
% !TEX spellcheck = it-IT

%************************************************

%************************************************


Consumers are increasingly relying on messaging apps for all types of communication weather it may be personal or business.
Shifting the way we interact with technology from commands to conversations will reshape digital experiences. It will enable organizations to reduce operational costs and identify new revenue opportunities and business models. Sometimes customers have some doubts during online payments and at that time they need someone to sort out their doubts, and this conversation can be easily fulfilled by messaging apps. Increasingly customers are using messaging applications and online chatting application to find and select products and services and to complete the payment process, all without having to mail or even to visit the particular brand website. 

The culture of online internet marketing is increasing day by day and this culture is being accepted by the customers. In favor to promote this new culture the messaging apps are also covering the gap and building a common platform where the customers and companies get the best way of conversation to get their deals done and get some profitable outcome. Everyone knows how to use messaging platforms, so there is nothing to relearn. Instead of having to switch to a web page to complete a payment, conversational commerce lets you transact right inside the messaging interface. This makes for a smoother, more effortless user and customer experience \cite{piyush2016}. Why should one build a bots ? Messaging platforms are the new browsers and bots are the new websites. This is a great opportunity to connect with your audience in a one on one and yet scalable manner.

Conversational agents have great business potential for several reasons. They provide a safe platform for transaction and a natural way of online marketing. Conversational commerce has a lot of future scope and it will grow the business environment of marketing. It gives you the platform for direct interaction between the customer and the company personas.

Conversational agents have brought a new revolution in field of business and marketing, It gives a better experience to both the seller as well as customers also and it saves time as well as money. Nowadays about days 52\% of the population prefer online shopping rather than mall or shop visit purchasing \cite{piyush2016}.

It's all about giving customers a reliable and easy platform to save their time and to make them feel better. It has been found that there are more than 2 billion Smartphone users in the world and they increasingly day by day are getting addicted to Smartphone and can't spend much time without them. And no wonder there is a growing interest in conversational agents \cite{piyush2016}.